Master's Project Journal

### 2019-04-21 thesis/Conclusion.tex
start of conc

\section{Conclusions}
\section{Suggested Future Work}
\subsection{\acl{TDL} Characterisation}
\acreset{TDL}
As previously mentioned, characterisation of the \ac{TDL} was not carried out due to the time it would have taken to perform the required measurements and tests. This characteristion can be accomplished through the use of an off-chip tunable delay. Off-chip is unfortunately a requirement, as the only delays available of the order required to test the step sizes are the variable delay of the inverters themselves. A resistor \& capacitor delay circuit can be used to perform these test, and the output of the \ac{PFD} analysed on a mixed-signal oscilloscope alongside the delayed and reference waveforms. The use of an off-chip delay element necessitates careful construction/cailbration of the measurement environment to eliminate the delay stemming from the signal path through input/output buffers as it leaves the chip.

@@

\subsection{\acs{FPGA} Clocked, Linear Period \acs{DCO}}
\acreset{FPGA,DCO}
While this design of \ac{DCO} was proposed earlier in this thesis, it was not implemented in any \ac{ADPLL}s, as it was only realised that the output waveform did not matter, just the location of the rising edges was not made until later in the project, once the pitfall encountered in the clocked \ac{PFD} design was resolved. Until this point the non-square wave output had eliminated the design from consideration. However, as in an \ac{ASIC} linear period designs are easier to implement, it would be ideal to have the benefit of frequency scaled hardware simulations with a \ac{DCO} that more closely relates the the eventual system.

>>>>

\section{Conclusions}
%TODO dont reset acro
The objective of this project was to create \iac{FPGA} based platform that could be used to prototype and model \ac{ADPLL} networks in a cost and time effective manner. The main effort of the project was to analyse the ways in which the components of an \ac{ADPLL} network could be designed, then select from this pool a number of the most appropriate designs. A number of \ac{ADPLL} designs were then created using the selected components in different combinations for the purposes of comparison. Once these \ac{ADPLL} designs had been validated, they were implemented in networks of a 2x2 and 3x3 Cartesian grid topology. Measurements and performance benchmarks were then carried out on these \ac{ADPLL} networks, and the results used to verify claims made regarding the intended use cases of the individual \ac{ADPLL} designs. Finally various small modifications to the \ac{ADPLL} designs were made, and their impact on system performance identified.

%TODO did I manage this?

\section{Suggested Future Work}
\subsection{\acl{TDL} Characterisation}
\acreset{TDL}
As previously mentioned, characterisation of the \ac{TDL} was not carried out due to the time it would have taken to perform the required measurements and tests. This characteristion can be accomplished through the use of an off-chip tunable delay. Off-chip is unfortunately a requirement, as the only delays available of the order required to test the step sizes are the variable delay of the inverters themselves. A resistor \& capacitor delay circuit can be used to perform these test, and the output of the \ac{PFD} analysed on a mixed-signal oscilloscope alongside the delayed and reference waveforms. The use of an off-chip delay element necessitates careful construction/cailbration of the measurement environment to eliminate the delay stemming from the signal path through input/output buffers as it leaves the chip.

@@

\subsection{\acs{FPGA} Clocked, Linear Period \acs{DCO}}
\acreset{FPGA,DCO}
While this design of \ac{DCO} was proposed earlier in this thesis, it was not implemented in any \ac{ADPLL}s, as it was only realised that the output waveform did not matter, just the location of the rising edges was not made until later in the project, once the pitfall encountered in the clocked \ac{PFD} design was resolved. Until this point the non-square wave output had eliminated the design from consideration. However, as in \iac{ASIC} linear period designs are easier to implement, it would be ideal to have the benefit of frequency scaled hardware simulations with \iac{DCO} that more closely relates the the eventual system.
